Abstract

### 2025-10-06 output/Main_text.Rmd
Use rectangular coordinates for coordinate plot
Instead of transforming the items to the latent space grid, represent their coordinates on a rectangular grid (i.e. the canonical basis)

@@

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     3
#| fig.width:      6.65
#| warning:        false
plot_orth_uncorr_contours + plot_oblique_ts

ggsave(file.path(DOC_DIR, "Figure_1.svg"))
```

>>>>

```{r compose-test-space-orthogonal-plot}
```

```{r compose-rectangular-cov-based-plot}
```

@@

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     4.7
#| fig.width:      6.65
#| warning:        false
(plot_orth_uncorr_contours + plot_orth_corr) /
  (plot_oblique_ts + plot_cov_based_orth) +
  plot_layout(guides = "collect")

ggsave(file.path(DOC_DIR, "Figure_1.svg"), width = 6.65, height = 4.7)
```
